---
title: "Gwinnett County Covid Data Cleaning"
date: "9/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r include=FALSE}
library(janitor)
library(tabulizer)
library(dplyr)
library(knitr)
library(magrittr)
library(purrr)
library(readr)
library(here)
```

# Overall table

## Function: overall table cleaning function 
```{r echo=FALSE}
clean_overall_table <- function(x) {
  x <-
  data.frame(x[[1]]) %>% 
  row_to_names(row_number = 1)
  if(ncol(x) == 4) {
    colnames(x) <- c("Reason", "Staff", "Student", "Total")
  } else {
    colnames(x) <- c("Reason", "Total")
  }
  x
}
```

## Existing Data

### Pull all tables
```{r echo=FALSE}
pdf_09_04 <- extract_tables("http://publish.gwinnett.k12.ga.us/gcps/wcm/connect/2d402f08-522f-4cc9-83f2-535726422841/9.4.2020-Local-School-COVID-19-Reporting-Daily-Report.pdf?MOD=AJPERES")
pdf_09_03 <- extract_tables("http://publish.gwinnett.k12.ga.us/gcps/wcm/connect/d9d665d9-18b2-46fd-80bd-3bc7df7d6f58/9.3.2020-Local-School-COVID-19-Reporting-Daily-Report.pdf?MOD=AJPERES")
pdf_09_02 <- extract_tables("http://publish.gwinnett.k12.ga.us/gcps/wcm/connect/09a1e3b6-46ed-48f9-bc4a-061e54c50471/9.2.2020-Local-School-COVID-19-Reporting-Daily-Report.v2.pdf?MOD=AJPERES")
pdf_09_01 <- extract_tables("http://publish.gwinnett.k12.ga.us/gcps/wcm/connect/1f516db8-e7ef-4919-8c96-65447d83171c/9.1.2020-Local-School-COVID-19-Reporting-Daily-Report-v2.pdf?MOD=AJPERES")
pdf_08_31 <- extract_tables("http://publish.gwinnett.k12.ga.us/gcps/wcm/connect/069e1e6e-0642-4607-913f-ed1d94e0d1bc/8.31.2020-Local-School-COVID-19-Reporting-Daily-Report.eq.pdf?MOD=AJPERES")
pdf_08_28 <- extract_tables("http://publish.gwinnett.k12.ga.us/gcps/wcm/connect/10e3c4a0-157b-4f3a-94c3-2f1a09a8d0e1/8.28.2020-Local-School-COVID-19-Reporting-Daily-Report.eq.pdf?MOD=AJPERES")
pdf_08_26 <- extract_tables("http://publish.gwinnett.k12.ga.us/gcps/wcm/connect/c32f8f78-8d6a-495e-975e-e75d5f7327a6/8.26.2020-Local-School-COVID19-Reporting-Daily-Report.eq.pdf?MOD=AJPERES")
pdf_08_25 <- extract_tables("http://publish.gwinnett.k12.ga.us/gcps/wcm/connect/52071556-0d5a-4118-b073-6acd0a5e62f0/8.25.2020-Local-School-COVID-19-Reporting-Daily-Report.eq.pdf?MOD=AJPERES")
pdf_08_24 <- extract_tables("http://publish.gwinnett.k12.ga.us/gcps/wcm/connect/50e67bcc-6e9a-4677-b83f-f8ffcc77b611/8.24.2020-Local-School-COVID-19-Reporting-Daily-Report.pdf?MOD=AJPERES")
pdf_08_21 <- extract_tables("http://publish.gwinnett.k12.ga.us/gcps/wcm/connect/e271ac1d-1f66-4f73-9429-54106cf65de0/8.21.2020-Local-School-COVID-19-Reporting-Daily-Report.pdf?MOD=AJPERES")
pdf_08_20 <- extract_tables("http://publish.gwinnett.k12.ga.us/gcps/wcm/connect/fc8ccad8-d591-4230-84c8-44be4dc89a10/8.20.2020-Local-School-COVID-19-Reporting-Daily-Report.eq.pdf?MOD=AJPERES")
pdf_08_19 <- extract_tables("http://publish.gwinnett.k12.ga.us/gcps/wcm/connect/4c44b0d3-866b-4112-abd4-e3b0d54442ed/8.19.2020-Local-School-COVID-19-Reporting-Daily-Report.eq.pdf?MOD=AJPERES")
pdf_08_18 <- extract_tables("http://publish.gwinnett.k12.ga.us/gcps/wcm/connect/e1e3ea68-4240-4b38-a0d4-9fd685971820/8.18.2020-Local-School-COVID-19-Reporting-Daily-Report.eq.pdf?MOD=AJPERES")

```

### Run cleaning function on all tables 
```{r}
pdf_table_names <- list(pdf_08_18, pdf_08_19, pdf_08_20, pdf_08_21, pdf_08_24, pdf_08_25, pdf_08_26, pdf_08_28, pdf_09_01, pdf_09_02, pdf_09_04)

all_days <- map_dfr(pdf_table_names, clean_overall_table) 
```

### Make dates table to bind 
```{r}
dates <- rep(seq(as.Date("2020-08-18"), Sys.Date(), by = "day"), each = 4)
dates <- data.frame(dates[!weekdays(dates) %in% c('Saturday','Sunday')]) 
colnames(dates) <- c("date")
dates <- filter(dates, 
                date != as.Date("2020-08-27"), 
                date != as.Date("2020-08-31"), 
                date != as.Date("2020-09-03"))
```


### Make reasons table to bind (since this is not clean for several of the days)
```{r}
rep_times <- (nrow(all_days)/4)
reasons <- rep(c("Close Contact", "Positive Case", "Suspected Case", "Total"), rep_times)
reasons <- data.frame(reasons)
```


### bind table with dates and reasons 
```{r}
all_days <- cbind(all_days, dates, reasons)
```


### manually clean the days where tabulizer crapped out
```{r}
nearly_all_days_clean <- 
  all_days %>% 
  mutate(Total = gsub(" ", "", Total), 
         date = as.character(date), 
         Total = 
           case_when(date == "2020-08-18" & reasons == "Close Contact" ~ 17, 
                     date == "2020-08-18" & reasons == "Suspected Case" ~ 21, 
                     date == "2020-08-18" & reasons == "Total" ~ 41,
                     date == "2020-08-25" & reasons == "Close Contact" ~ 19, 
                     date == "2020-08-25" & reasons == "Suspected Case" ~ 18, 
                     date == "2020-08-25" & reasons == "Total" ~ 42,
                     date == "2020-08-26" & reasons == "Close Contact" ~ 20, 
                     date == "2020-08-26" & reasons == "Suspected Case" ~ 18, 
                     date == "2020-08-26" & reasons == "Total" ~ 38,
                     date == "2020-09-02" & reasons == "Close Contact" ~ 103, 
                     date == "2020-09-02" & reasons == "Positive Case" ~ 2, 
                     date == "2020-09-02" & reasons == "Suspected Case" ~ 33, 
                     date == "2020-09-02" & reasons == "Total" ~ 138,
                     TRUE ~ as.numeric(Total))) %>% 
  select(date, reasons, Staff, Student, Total)
```


### manually make the two days where tabulizer really totally crapped out
```{r}
messy_days <- data.frame(
date = c("2020-08-27", "2020-08-27", "2020-08-27", "2020-08-27", 
         "2020-08-31", "2020-08-31", "2020-08-31", "2020-08-31", 
         "2020-09-03", "2020-09-03", "2020-09-03", "2020-09-03"), 
reasons = c("Close Contact", "Positive Case", "Suspected Case", "Total", 
            "Close Contact", "Positive Case", "Suspected Case", "Total", 
            "Close Contact", "Positive Case", "Suspected Case", "Total"), 
Staff = c(31, 0, 16, 47, 18, 1, 15, 34, 30, 0, 23, 53), 
Student = c(54, 2, 16, 72, 64, 0, 16, 80, 60, 0, 39, 99), 
Total = c(85, 2, 32, 119, 82, 1, 31, 114, 90, 0, 62, 152)
)

```

### bind messy days with all others
```{r}
all_days_clean <- rbind(nearly_all_days_clean, messy_days)
```


```{r}
write_csv(all_days_clean, here::here("data/clean/all_days_clean_overall.csv"))
```


## Pull and add a new day 
```{r}
latest_day <- extract_tables("http://publish.gwinnett.k12.ga.us/gcps/wcm/connect/2d402f08-522f-4cc9-83f2-535726422841/9.4.2020-Local-School-COVID-19-Reporting-Daily-Report.pdf?MOD=AJPERES")
clean_overall_table(latest_day)

missing_latest_day <- read_csv(here::here("data/clean/all_days_clean_overall.csv"))

rbind(missing_latest_day, latest_day)
write_csv(all_days_clean, here::here("data/clean/all_days_clean_overall.csv"))
```

# Clean latest day detailed report
```{r}
new_cases_by_school_p1 <- data.frame(latest_day[[2]]) %>% 
  # select(-X3, -X5, -X7) %>% 
  # rename(X3 = X4, X4 = X6, X5 = X8) %>% 
  mutate(X1 = as.character(X1),
         X2 = as.character(X2),
         X3 = as.character(X3),
         X4 = as.character(X4),
         X5 = as.character(X5))
  #        X3 = ifelse(X1 == "School", "Positive Case", X3), 
  #        X4 = ifelse(X1 == "School", "Suspected Case", X4), 
  #        X5 = ifelse(X1 == "School", "Total", X5), 
  #        X1 = ifelse(X1 == "School", "School", X1), 
  #        X2 = ifelse(X2 == "School", "Close Contact", X2))
  
new_cases_by_school_p2 <- data.frame(latest_day[[3]]) %>% 
    mutate(X1 = as.character(X1),
         X2 = as.character(X2),
         X3 = as.character(X3),
         X4 = as.character(X4),
         X5 = as.character(X5))

new_cases_by_school <- rbind(new_cases_by_school_p1, new_cases_by_school_p2) %>% 
  row_to_names(row_number = 1) %>% 
  clean_names() %>% 
  filter(school != "Science and Technology", 
         school != "School") %>% 
  mutate(school = as.character(school), 
         school = ifelse(school == "Gwinnett School of Mathematics,", "Gwinnett School of Mathematics, Science and Technology", school), 
         positive_case = as.numeric(positive_case), 
         suspected_case = as.numeric(suspected_case),
         close_contact = as.numeric(close_contact))

write_csv(new_cases_by_school, here::here("data/clean/new_cases_by_school.csv"))
```

